Semi-supervised author disambiguation for large and partially annotated databases of scientific publications

### 2015-07-14 paper.tex
table of contents
abstract

\documentclass{article}

% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

@@

\usepackage[accepted]{icml2015}

@@

\icmltitlerunning{Semi-supervised author disambiguation for scientific publications}

@@

\twocolumn[
\icmltitle{Semi-supervised author disambiguation for scientific publications}

\icmlauthor{Gilles Louppe}{g.louppe@cern.ch}
\icmlauthor{Hussein Al-Natsheh}{}
\icmlauthor{Mateusz Susik}{}
\icmladdress{CERN, CH-1211 Geneva 23, Switzerland}

\icmlkeywords{variable importances, random forest}

\vskip 0.3in
]

\begin{abstract}
The purpose of this document is to provide both the basic paper template and
submission guidelines.
\end{abstract}

% Background ==================================================================

\section{Background}
\label{background}

@@

\section{Methods}
\label{methods}

@@

\section{Results and discussion}
\label{results}

@@

% References ==================================================================
\nocite{langley00}

\bibliography{bib}
\bibliographystyle{icml2015}

>>>>

\documentclass[11pt]{article}
\usepackage[margin=1.2in]{geometry}

% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}
\usepackage{color}

@@

\usepackage{titlesec}
\titleformat{\section}{\sf\large}{\thesection.}{1em}{}
\titleformat{\subsection}{\sf}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\sf \small}{\thesubsubsection}{1em}{\it }

\newcommand{\glnote}[1]{\textcolor{red}{GL: #1}}

@@

\title{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
\author{Gilles Louppe, Hussein Al-Natsheh and Mateusz Susik\\
       \it{CERN, Geneva, Switzerland}}

\date{}

%\icmltitlerunning{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}

@@

\maketitle

\begin{abstract}

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is difficult because (i) an author may use different spellings,
variants or synonyms across her career and/or (ii) distinct authors may share
the same name. Among solutions ot this problem, digital libraries are
increasingly offering tools for authors to manually curate their publications
and claim which ones are theirs. Indirectly, these tools allow for the
inexpensive collection of large annotated training data that can be further
leveraged to improve the overall accuracy of the system. In this context, we
propose a semi-supervised machine learning disambiguation solution in the case
large and partially annotated databases of scientific publications. We describe
how this annotated data can be used to learn an accurate classifier for
identifying corefering authors, guide the clustering of scientific publications
by distinct authors and finally match the resulting clusters to existing
profiles. Evaluation is carried out on a real-world database of 1 million
annotated publications and demonstrates the very good accuracy of the proposed
solution. In particular, our analysis of parameters and features reveal that...
\glnote{To be completed with actual results.}

\end{abstract}

% Introduction ==================================================================

\section{Introduction}
\label{introduction}

% general introduction to the disambiguation issues
% summary of what we did
% outline of the paper

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
Vivamus consequat cursus auctor.

% Related works ==================================================================

\section{Related works}
\label{relate-works}

% levin

@@

\section{Semi-supervised author disambiguation}
\label{methods}

\subsection{Overview}
% figure, notations, etc

\subsection{Distance learning}
% distance learning as a supervised problem
% balancing difficult and easy cases

\subsection{Blocking}
% motivation
% last name, first initial
% phonetics something (dm)

\subsection{Semi-supervised clustering}
% hierarchical clustering
% semi-supervised clustering
% cold start problem (when no labels in a block)

\subsection{Matching}
% general description in a real system

% Implementation ======================================================

\section{Implementation}
\label{implementation}

@@

\section{Experiments}
\label{experiments}

\subsection{Data}
% source of the data, labels in the data, etc
% release the data

\subsection{Evaluation protocol}
% measures (b^3, paired, size of clusters)
% training / valid / test sets

\subsection{Distance learning}
% feature engineering
% variable importance analysis
% supervised learning model

\subsection{Blocking}

\subsection{Semi-supervised clustering}
% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions
% talk about impact of small improvements in terms of citations statistics

@@

% future improvements

% References ==================================================================
\nocite{langley00} % todo remove

\bibliographystyle{apalike}
\bibliography{bib}
